Multi-EWAS enrichment example

### 2024-01-17 figs/multi_ewas_example.Rmd
randomisation test

>>>>

## Randomise data

To demonstrate that mitch is robust to false positives, we can perform
randomisation of the data.

```{r,randomise}

fres <- lapply(1:100,function(i){
  seed=i*1000
  z <- lapply(l2,function(m) {
    m=l2[[1]]
    set.seed=sum(m$Beta)*seed ; m$Beta <- sample(x=m$Beta,replace=FALSE,size=752722)
    m2 <- mitch_import(x=m,DEtype="prescored",geneTable=gt,geneIDcol="CpG")
    mres <- mitch_calc(x=m2,genesets=gs_symbols,minsetsize=5,cores=1, priority="effect")
    mtable <- mres$enrichment_result
    nrow(subset(mtable,p.adjustANOVA<0.05))
  })
  sum(unlist(z))
})

fres <- unlist(fres)
summary(fres)
